---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# bitmexr: R Client for the BitMEX Exchange

[![Travis build status](https://travis-ci.org/hfshr/bitmexr.svg?branch=master)](https://travis-ci.org/hfshr/bitmexr)

# Overview

The goal of `bitmexr` is to provide an API wrapper for cryptocurrency derivatives exchange [BitMEX](https://www.bitmex.com/). Specifically, it can help R users access price/trade data across the many products available on the exchange, which can then be used for further analysis. For more information about the API, check https://www.bitmex.com/app/apiOverview.

# Installation

The development version of `bitmexr` can be installed from github:

```{r eval=FALSE, include=TRUE}
# install.packages("devtools")
devtools::install_github("hfshr/bitmexr")
```

# Package contents

The package as two main functions:

- `trades()` returns individual trade data for a specified symbol/time period
- `bucket_trades()` returns bucketed trade data (open, high, low, close) for either 1 minute, 5 minute, 1 hour or 1 day time frames for a specified symbol.
    
The package also contains map_* variants of these functions (`map_trades()` and `map_bucket_trades()`) which create and send multiple API requests when the total length of the data desired is greater than the 1000 row limit in a single API request.

# Examples

Simple price data for the most recent trades on the exchange:

```{r message=FALSE}
library(bitmexr)
library(dplyr)

# 1000 for most recent trades on the exchange for "XBTUSD"

trades(symbol = "XBTUSD") %>% 
  select(timestamp, symbol, side, size, price) %>% 
  head()

```

Get all bucketed trade data (hourly binSize) between January 2019 and January 2020. 

```{r}

map_bucket_trades(start_date = "2019-01-01", 
                  end_date = "2020-01-01", 
                  binSize = "1h",
                  symbol = "XBTUSD") %>% 
  select(1:6) %>% 
  head()

```


# What the package _does not_ do

The package is designed to simply obtain trade data from the exchange for further analysis/visualisation within R.
However the BitMEX API can do far more than what is implemented within this package. For more information please see [https://www.bitmex.com/app/apiOverview](https://www.bitmex.com/app/apiOverview).
Currently, the package does not support any of the API requests requiring authentication (e.g., obtaining trade data for personal account, posting/executing trades etc), however this may change in the future.

# Disclaimer

This software is in no way affiliated, endorsed, or approved by the
[BitMEX cryptocurrency exchange](https://www.bitmex.com) or any of its affiliates. 

# Contribution

If you spot any issues, or would like additional features added, pleases feel free raise and issue or submit a pull request.

# Code of Conduct

Please note that this project is released with a [Contributor Code of Conduct](CODE_OF_CONDUCT.md). 
By participating in this project you agree to abide by its terms.




