---
title: "Placing and managing orders with bitmexr"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{placing-orders}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(bitmexr)
```

`bitmexr` now supports placing, editing and cancelling orders on both the testnet API and live API provided by BitMEX. This vignette outlines how you can use `place_order()`, `edit_order()` and `cancel_order()` to manage your BitMEX trading directly from R! For more information about the API please visit (https://www.bitmex.com/app/apiOverview)

The following examples will use the tn_* varients of the managing trades functions (`tn_place_order()`, `tn_edit_order()` and `tn_cancel_order()`) to access the testnet API. These functions will work in exactly the same way when using the live API (without the tn_ prefix).

# Placing orders

Use the following to place an order on the exchange

```{r eval=FALSE}
tn_place_order(symbol = "XBTUSD", 
               orderQty = 10, 
               price = 5000)
```

If `price` is not specified, a market order will be used.

```{r eval=FALSE}
tn_place_order(symbol = "XBTUSD", 
               orderQty = 10)
```

You can specific `side = Sell` or use a negative `orderQty` to initiate a sell order.

```{r eval=FALSE}
tn_place_order(symbol = "XBTUSD", 
               orderQty = -10, 
               price = 10000)
```

Use `?tn_place_order()` or `?place_order()` to see the full list of order options, or visit 
https://www.bitmex.com/api/explorer/#/Order

# Editing orders

Once an order has been placed, it is possible to edit the order using either the `orderID` returned when using `place_order()` or the custom client order id specified using `clOrdID`.

For example placing the following order:

```{r eval=FALSE}
tn_place_order(symbol = "XBTUSD", 
               orderQty = 100, 
               price = 5000, 
               clOrdID = "mybigorder")
```

Could be edited using:

```{r eval=FALSE}
tn_edit_order(origClOrdID = "mybigorder", 
              price = 4000)
```

# Cancel orders

Cancelling order is very similar to editing order, simply use the orderID or clOrdID 

```{r eval=FALSE}
tn_cancel_order(clOrdID = "mybigorder")
```

It is also possible to cancel all orders. For example cancel all sell orders using:

```{r eval=FALSE}
tn_cancel_all_orders(filter = '{"side": "Sell"')
```

# Extra

The `get_bitmex` and `post_bitmex` functions can be used to access additional API endpoints that do not have a dedicated wrapper.

The `path` argument is the API endpoint and always starts with a "/" (e.g., "/chat").
The `args` argument is a named list of valid parameter values to pass to the API endpoint. These are well documented on https://www.bitmex.com/api/explorer/ 

For example, to access the user information for your testnet account you can use:

```{r eval=FALSE}
tn_get_bitmex(path = "/user", use_auth = TRUE)
```

As this is a private API endpoint, authentication was required.

A POST example to increase the leverage on a position is:

```{r eval=FALSE}
tn_post_bitmex(path = "/position/leverage", 
               args = list("symbol" = "XBTUSD", 
                           "leverage" = 10))
```

Please use the https://www.bitmex.com/api/explorer/ to view all possible API endpoints.
